A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-28 rr-flow.Rmd
added some intro prose

author: 
  - name          : "Aaron Peikert"
    affiliation   : "1,2"
  - name          : "Andreas Brandmaier"
    affiliation   : "1,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    email         : "brandmaier@mpib-berlin.mpg.de"

@@

! TODO - Unterschied zwischen computational, empirical, and statistical reproducibility (cf. Stodden et al., 2014)

>>>>

author: 
  - name          : "Aaron Peikert"
    affiliation   : "1,2"
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    email         : "brandmaier@mpib-berlin.mpg.de"

@@

In this tutorial, we describe a principled workflow to ensure long-term reproducibility of
R-based data analyses. In this context, reproducibility means to us that scientific results together with their computational scientific workflows are reported fully, transparently and sustainably available, such that the workflow can be re-run by a different person and/or later in time and the results will be identical to the ones intially reported. Here, we combine four tools from the computer sciences, whose interplay can guarantuee full and sustainable computational reproducibility of data analyses. The major four elements are:
